---
title: "Case_Study_bellabeat"
author: "Gustavo Venceslau"
date: "2023-11-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)

```

## BELLABEAT use for nutrition plans follow up

This study aims to answer the following questions:

Are users inputting weight data in the app?

How often are they collecting weight data?

Are users using the app as a supportive tool for their nutrition plan or diet?

For this study the weightLogInfo_merged dataframes were used.



```{r echo=FALSE}
###                    Importing and preparing Weight data
##      Weight data from eight of the thirty three app users 
weightLogInfo_merged <- read_csv("C:/Users/gusta/OneDrive/Documentos/Week 8 - Case Study/Fitabase Data 4.12.16-5.12.16/weightLogInfo_merged.csv")
# Separate Date into Date and time
weightLogInfo_merged <- separate(weightLogInfo_merged, Date, into = c('Date', 'Time'), sep = ' ')


## Counting the number of distinct participants
# Count the number of distinct values in the Id column
distinct_count <- weightLogInfo_merged %>%
  summarise(distinct_count = n_distinct(Id))


##      Preparing the data to plot by participant.
# Function to label distinctively each element of a column.
label_distinctively <- function(column) {
  #Convert the column to a factor with unique labels
  factor(column, labels = seq_along(unique(column)))
}
# Apply the function to the Id column
weightLogInfo_merged$DistinctLabel <- label_distinctively(weightLogInfo_merged$Id)


```



## The available Weight data

The graph shows the number of the app users that have input weight data during the period of observation (from 04/12/206 to 05/12/2006). 


It seems that users are not using the app for weight control. 


The total weight data available comes from eight out of thirty three users.

```{r echo=FALSE}

ggplot(data=weightLogInfo_merged, aes(x=DistinctLabel, y=WeightKg, color = IsManualReport))+
    geom_jitter(width = 0.2)+
  labs(x = "App Users", y = "Weight (Kg)")+
  theme(axis.text.x = element_text(angle = 0), legend.position = "bottom")

```

## Detailing user Weight data over time

Few users are consistently inputting weight data over time. Two users have consistently input weight data in the period.

```{r echo=FALSE}

p <-ggplot(data=weightLogInfo_merged, aes(x=Date, y=WeightKg, color = IsManualReport))+
  #geom_point()+
  theme(axis.text.x = element_blank(), legend.position = "bottom")+ 
  geom_jitter(width = 0.2)+
  labs(x = "Date", y = "Weight (Kg)")
## Graph time vs. calories

p + facet_wrap(vars(Id), nrow = 4)
```


## Facet Ploting Weight data


Looking at the data of the two users that consistently collected weight data, it is possible to see that they are working on losing weight. 

This indicate that they are following a nutritional plan or a diet.

``` {r echo=FALSE}

# Filtering data by specific values then plot

df <- weightLogInfo_merged

#Values to match in the 'Id' column
values_to_mach <- c("6962181067", "8877689391")

# Filter rows that match the specified values
matching_rows <- df[df$Id %in% values_to_mach, ]
#view(matching_rows)

# Plot the matching rows


ggplot(data = matching_rows, aes(x = Date, y = WeightKg, group = DistinctLabel, color = DistinctLabel))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE, col = "green")+
  theme(axis.text.x = element_text(angle = 90, size = 0.5), legend.position = "bottom")+ 
  labs(y = "Weight (Kg)")+
  facet_wrap(vars(Id), scales = "free_y", nrow = 2, strip.position = "top") 

ggplot(data = matching_rows, aes(x = DistinctLabel, y = WeightKg))+
  geom_boxplot(aes(colour = DistinctLabel))+
    labs(x = "Users", y = "Weight (kg)", color = "User")+ 
  theme(legend.position = "none")+
  facet_wrap(vars(Id), scales = "free_y", nrow = 1, strip.position = "top") 



```






From the previous data and graphs, it is possible to conclude that Bellabeat can expand its use as a weight control tool.


One can think of a slogan: "Bellabeat is your best weight confidence friend!"



:)